Wibbly Wobbly Timely Wimely Questions: \\Classifying Timely And Timeless Questions

### 2021-09-18 paper/main.tex
Addressed comment 5, motivating answer filtering

After getting an answer for each year, we hypothesized that a timely question
would have answers that change year to year, while a timeless question would
have similar answers no matter which year was used as the context. However,
before we could identify changes with the answers, we had to account for errors
with the model’s ability to answer questions. First, we removed any questions in
which any of the answers returned a page that did not exist, or was redirected.
Although a page that did not exist could indicate a timely question, we decided
to remove those in case there was a problem with the Wikipedia link or the
model. \begin{figure*}[ht]
	\begin{center}
		\includegraphics[width=5in]{timeless leven.png}
		\includegraphics[width=5in]{timely leven.png}
		\includegraphics[width=5in]{leven false pos.png}
		\includegraphics[width=5in]{leven_false_neg.PNG}
	\end{center}
	\caption{Levenshtein Examples (top is timeless, middle is timely, third is false positive, bottom is false negative).}
	\label{fig:levenshtein_examples}
\end{figure*}

After this initial filtering, our subset of 20,000 questions and answers was
reduced to 10,183 samples. Then, using the string Levenshtein distance, we
calculated the difference of each answer to the correct short answer provided in
the NQ dataset. Some questions had multiple correct short answers, in which case
we compared to the ground truth that had the closest match to the predicted
answer. Any samples which had an incorrect answer using the predicted answer
from the original HTML in the question were filtered out from our data. We
defined an incorrect answer as having a string comparison score of at least 70.
After removing these samples, we were left with a dataset of 3,408 samples to
work with.

>>>>

After getting an answer for each year, we hypothesized that a timely question
would have answers that change year to year, while a timeless question would
have similar answers regardless of the context's year. However, before we could
identify changes with the answers, we had to account for model errors.
Conceptually, the answer filtering step removes questions where
model/methodology error could contribute to high answer variance. In filtering
these questions out, we could more confidently attribute variance to timeliness.
We defined model/methodology error as Wikipedia page-retrieval failure at any
timestamp and/or the model's inability to output the ground truth answer using
the most current Wikipedia page. This sought to reduce confounding variables in
answer variance and create a more accurate classifier.

As mentioned, we removed any questions where Wikipedia retrieval returned a page
that did not exist, or was redirected. Although a previously non-existent page
could indicate a timely question, we decided to remove those in case there was
a problem with the Wikipedia link or the model. After this initial filtering,
our subset of 20,000 questions and answers was reduced to 10,183 samples.
\begin{figure*}[ht]
    \begin{center}
        \includegraphics[width=5in]{timeless leven.png}
        \includegraphics[width=5in]{timely leven.png}
        \includegraphics[width=5in]{leven false pos.png}
        \includegraphics[width=5in]{leven_false_neg.PNG}
	\end{center}
  \caption{Levenshtein Examples (top is timeless, middle is timely, third is false positive, bottom is false negative).}
  \label{fig:levenshtein_examples}
\end{figure*}

Next, because the SQuAD model wasn't pretrained on the NQ dataset, we tested the
model's ability to correctly answer the question using NQ's original HTML. Using
the string Levenshtein distance, we calculated the difference between each
model-predicted answer and the NQ dataset's ground truth short answer. Some
questions had multiple correct short answers, in which case we compared to the
ground truth that had the closest match to the predicted answer. Any samples
which had an incorrect answer using the predicted answer from the original HTML
in the question were filtered out from our data. We defined an incorrect answer
as having a string comparison score of at least 70. After removing these
samples, we were left with a dataset of 3,408 samples to work with.
